Neural Textures make Better Simulators ``I can't believe it's not real!"

### 2022-06-11 CORL/example.tex
Moved texture realism theory to appendix

We can improve the translation results by forcing the neural texture to look realistic, instead of allowing it to have arbitrary colors.

@@

Texture realism loss equation:
$L_{TR}=L_{TR_{l2}}+L_{TR_{msssim}}$
where 
$L_{TR_{msssim}} = -msssim(\pi,\hat{p})$ and
$L_{TR_{l2}} = \frac{
	\sum\limits_{i=1}^B {
	   %  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
	   \left( \pi-\hat{p}  \right)^2
		} 
   }
   {B}$

@@

\section{Appendix} 
Also, the resolution of the unprojection matters:

@@

>>>>

We can improve the translation results by forcing the neural texture to look realistic, instead of allowing it to have arbitrary colors.
To do this we add an image similarity loss that makes $\pi$ look like its translation $\hat{p}$.

@@

@@

\section{Appendix} 
\label{sec:appendix}

	\subsection*{Unprojection Recovery Resolution Effect}

		Also, the resolution of the unprojection matters:

@@

	\subsection*{Texture Realism Theory}
		\label{sec:texture_realism_theory}
		Texture realism loss equation:
		$L_{TR}=L_{TR_{l2}}+L_{TR_{msssim}}$
		where 
		$L_{TR_{msssim}} = -msssim(\pi,\hat{p})$ and
		$L_{TR_{l2}} = \frac{
			\sum\limits_{i=1}^B {
			%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
			\left( \pi-\hat{p}  \right)^2
				} 
		}
		{B}$
